\documentclass[MTech]{iitddiss}
% \settopmatter{printacmref=false}

\input{macros}
\usepackage{t1enc}

\usepackage{graphicx}
\usepackage{hyperref} % hyperlinks for references.
\usepackage{amsmath} % easier math formulae, align, subequations \ldots
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{natbib}
\usepackage{fancyhdr}
 \linespread{1.2}

\pagestyle{fancy}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}

\fancyhf{}

\rhead{\fancyplain{}{\thepage}} % predefined ()
\lhead{\fancyplain{}{\rightmark}} % 1. sectionname, 1.1 subsection name etc
\cfoot{\textcopyright \text{ } \the\year, \emph{Indian Institute of Technology Delhi}}
\renewcommand{\footrulewidth}{0.4pt}
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title page

\title{Mining Top-$k$ Correlated Subgraphs in a Large Graph}

\author{Akshit Goyal}
\advisor{Prof. Sayan Ranu}
\entrynumber{2014CS50278}
\date{June 2019}
\department{Computer Science and Engineering}

%\nocite{*}
\maketitle


% \pagenumbering{arabic}

% \copyrightyear{2020}
% \acmYear{2020}
% \setcopyright{acmcopyright}
% \acmConference[SIGMOD '20]{ACM SIGMOD '20: ACM International Conference on Management of Data}{June 14--19, 2020}{Portland, Oregon, USA}
% \acmPrice{15.00}
% \acmDOI{10.1145/1122445.1122456}
% \acmISBN{978-1-4503-9999-9/18/06}

% \begin{document}

% \title{}

% \author{}
% \advisor{Sayan Ranu}
% \department{Computer Science and Engineering}

%\author{Arijit Khan} \affiliation{\institution{Nanyang Technological
%University}
%}
%\email{arijit.khan@ntu.edu.sg}
%
%\author{Arneish Prateek} \affiliation{\institution{Indian Institute of
%Technology Delhi, India}
%}
%\email{ch1140786@iitd.ac.in}
%
%\author{Sayan Ranu} \affiliation{\institution{Indian Institute of Technology
%Delhi, India}
%}
%\email{sayanranu@iitd.ac.in}
%
%\author{Akshit Goyal} \affiliation{\institution{Indian Institute of Technology
%Delhi, India}
%}
%\email{cs5140278@iitd.ac.in}

% \maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Certificate
\certificate

\vspace*{0.5in}

\noindent This is to certify that the thesis titled {\bf \LaTeX\ Mining Top-$k$ Correlated Subgraphs in a Large Graph}, submitted by {\bf Akshit Goyal},
  to the Indian Institute of Technology, Delhi, for
the award of the degree of {\bf Master of Technology}, is a bonafide
record of the research work done by him under our supervision.  The
contents of this thesis, in full or in parts, have not been submitted
to any other Institute or University for the award of any degree or
diploma.

\vspace*{1.5in}

\begin{singlespacing}
\hspace*{-0.25in}
\parbox{2.5in}{
\noindent {\bf Prof.~1} \\
\noindent Professor Sayan Ranu\\
\noindent Dept of CSE\\
\noindent IIT-Delhi, 110016 \\
}
\hspace*{1.0in}
\end{singlespacing}
\vspace*{0.25in}
\noindent \hfill Place: New Delhi\\
\noindent \hfill Date: June 25, 2019\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Acknowledgements

\acknowledgements

This thesis is the outcome of a joint collaborative effort with Arneish Prateek (Master's Candidate, IIT Delhi). The author of this thesis has attempted to demarcate the contributions of the collaborator and himself to the best of his abilities. For a complete guide to this project, this thesis must be read in conjunction with the thesis titled XYZ by Arneish Prateek. Appendix I contains the complementary sections from this other thesis. The following chapters are common to both theses:

\textbf{Chapter 1}

\textbf{Chapter 2}

\textbf{Chapter 3}: Sections 3.1,3.2,3.3,3.4

\textbf{Chapter 5}: Section 5.1



\begin{abstract}
Mining of correlated patterns, that represent an important class of
regularities, has become increasingly important in data management and
analytics. Surprisingly, the problem of correlated subgraphs mining from a
single, large graph has received little attention. We investigate a novel and
critical graph mining problem, called correlated subgraphs mining, which is
defined as a pair of subgraph patterns that frequently co-occur in proximity
within a single graph.

Correlated subgraphs are different from frequent subgraphs due to the
flexibility in which the constituent subgraph instances are connected, thus the
existing frequent subgraphs mining algorithms cannot be directly applied.
Furthermore, correlation computation between two subgraph patterns require
enumerating and finding distances between every pair of subgraph instances of
both these patterns --- which are both memory intensive and computationally
demanding. 

To this end, we design a novel, single-step, best-first exploration algorithm to
detect correlated subgraph patterns: To further improve the efficiency, we
develop a top-$k$ pruning strategy, while to reduce the memory footprints, we
develop a compressed data structure, called $\mathcal{R}$eplica that stores all
instances of a subgraph pattern. Our empirical results show that the proposed
algorithm not only finds interesting correlations, but also achieves good
performance for finding correlated subgraphs in large graphs.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table of contents etc.

\begin{singlespace}
\tableofcontents
\thispagestyle{empty}

% \listoftables
% \addcontentsline{toc}{chapter}{LIST OF TABLES}
% \listoffigures
% \addcontentsline{toc}{chapter}{LIST OF FIGURES}
\end{singlespace}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abbreviations
% \abbreviations

% \noindent
% \begin{tabbing}
% xxxxxxxxxxx \= xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
% \textbf{IITD}   \> Indian Institute of Technology, Delhi \\
% \textbf{RTFM} \> Read the Fine Manual \\
% \end{tabbing}

% \pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Notation

% \chapter*{\centerline{NOTATION}}
% \addcontentsline{toc}{chapter}{NOTATION}

% \begin{singlespace}
% \begin{tabbing}
% xxxxxxxxxxx \= xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
% \textbf{$r$}  \> Radius, $m$ \\
% \textbf{$\alpha$}  \> Angle of thesis in degrees \\
% \textbf{$\beta$}   \> Flight path in degrees \\
% \end{tabbing}
% \end{singlespace}

% \pagebreak
% \clearpage

% The main text will follow from this point so set the page numbering
% to arabic from here on.
\pagenumbering{arabic}

\vspace{-4mm}




\input{introduction}
\input{preliminaries}
\input{exact_algo}
\input{approx_algo}

% \input{overview} \input{searchTree} \input{calculation}
% \input{algorithm}
% \input{correlatedGroup}

\input{experiments}
\input{related}
\input{conclusions}

\appendix

\chapter{A SAMPLE APPENDIX}

Just put in text as you would into any chapter with sections and
whatnot.  Thats the end of it.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{-2mm}
{\scriptsize
\bibliographystyle{abbrv} %\enlargethispage*{3\baselineskip}
\bibliography{ref}
}


\end{document}


